Using Hybrid Machine Learning for Fundamental Stellar Parameter Inference

### 2024-05-10 paper/paper2_neo/paper.tex
Test 120-point inference

@@

advent of physics-informed machine learning.

>>>>

The spectral reconstruction process is done by iterating over the 
PHOENIX generator, evaluating each interpolator at the given coordinates, 
then reshaping the data into the same format that PyTorch uses for 
state dictionaries. During the iteration, if the interpolated
log-amplitude of the line is less than -100, the line is excluded from the 
state dictionary. Why -100 instead of -1000? This is because near the 
areas that we artificially populated, the manifold experiences artifacts due 
the sudden decline. We have to anticipate that decline and cut off the 
behavior in advance. This saves on computational time. Then, the state
dictionary is fed into \texttt{blase}'s \texttt{SparseLinearEmulator},
which reconstructs the spectrum by constructing a forward model based on 
the input state dictionary. Any \texttt{nan} values are set to 1 (which we 
can do because the spectra are all normalized), and the spectrum is 
complete.

@@

growing power of physics-informed machine learning.
